---
title: "Developing Data Products Course Project"
author: "Edgardo Di Bello"
date: "12/26/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***
### **Introduction**

This project consists of two parts

1. A Shiny application that has widget input, ui input in server.R, reactive output using server calculations, and supporting documentation.

2. A Reproducible Pitch Presentation that contains five slides in either Slidify or Rstudio Presenter that is pushed to and hosted on GitHub or Rpubs and contains embedded R code that runs.

### **Links**

1. Shiny App : [Link](https://edgardodibello.shinyapps.io/DevelopingDateProductsCourseProject/)

2. `server.R` and `ui.R` files: [Link](https://github.com/EdgardoDiBello/Developing-Data-Products-Course-Project)


## The App

My app is very simple, it consists of the analysis of the data `trees`, when entering the values of x and y and hitting the apply changes button, a graph of the relationship between the two data that was entered is created, and it is also possible to select a set of points greater than 2 within the graph to get the slope and intercept of the selected data.

## Example

graph of data trees relating girth against volume
```{r eval = FALSE}
data("trees")
plot(trees$Girth, trees$Volume, xlab = "Girth",
     ylab = "Volume", main = "Comparision between Girth vs Volume",
     cex = 1, pch = 19, col= "aquamarine")
        
  abline(lm(Volume ~ Girth, trees),col="darkviolet",lwd=2)
  
```

## Example

```{r echo = FALSE}
data("trees")
plot(trees$Girth, trees$Volume, xlab = "Girth",
     ylab = "Volume", main = "Comparision between Girth vs Volume",
     cex = 1, pch = 19, col= "aquamarine")
        
  abline(lm(Volume ~ Girth, trees),col="darkviolet",lwd=2)
  
```